Manuscript

### 2023-05-20 Manuscript.Rmd
updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms)

scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R")
q = lapply(here("scripts", scripts), source)
```

@@

```{r model recovery}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr)

scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R", "model recovery.R")
q = lapply(here("scripts", scripts), source)
```

@@

```{r model recovery}
########################################### Resorla wagner parameters:
mu_alpha = seq(0.1,0.3,length.out = 10)
kappa_alpha = 50
mu_w1 = seq(0.1,0.3,length.out = 10)
kappa_w1 = 50
sd_precision_percept = 0.5
sd_beta = 0.5
nsubs = 10
parameters = expand.grid(mu_alpha = mu_alpha,
                         kappa_alpha = kappa_alpha,
                         mu_w1 = mu_w1,
                         kappa_w1 = kappa_w1,
                         sd_precision_percept = sd_precision_percept,
                         sd_beta = sd_beta,
                         nsubs = nsubs)

parameters$id = 1:nrow(parameters)
data_list_rw <- split(parameters, parameters$id)

######################################## Weighted bayes

mu_alpha = rep(0.2,100)
kappa_alpha = 50
mu_w1 = 0.2
kappa_w1 = 50
mu_w2 = 0.2
kappa_w2 = 50
sd_percept_precision = 0.5
sd_beta = 0.5
nsubs = 50
parameters = expand.grid(nsubs = nsubs, 
                         mu_alpha = mu_alpha, 
                         kappa_alpha = kappa_alpha, 
                         mu_w1 =  mu_w1, kappa_w1 = kappa_w1,
                         mu_w2 = mu_w2, kappa_w2 = kappa_w2, 
                         sd_percept_precision = sd_percept_precision, 
                         sd_beta = sd_beta)
parameters$id = 1:nrow(parameters)
data_list_wb <- split(parameters, parameters$id)

######################################### Kalman

mu_sigmaEta = rep(50,100)
mu_sigmaPsi = 10
mu_sigmaEpsilon = 0.1
sd_sigmaEta = 0.1
sd_sigmaPsi = 0.1
sd_sigmaEpsilon = 0.1
nsubs = 50
parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
                         mu_sigmaPsi = mu_sigmaPsi,
                         mu_sigmaEpsilon = mu_sigmaEpsilon,
                         sd_sigmaEta = sd_sigmaEta,
                         sd_sigmaPsi = sd_sigmaPsi,
                         sd_sigmaEpsilon = sd_sigmaEpsilon,
                         nsubs = nsubs)
parameters$id = 1:nrow(parameters)
data_list_kalman <- split(parameters, parameters$id)

######################################### fit data_rw:
#loos = model_fitter_rwdata(data_list_rw[[1]])

data_list = data_list_rw[1:3]

plan(multisession, workers = 5)

rw_loo = furrr::future_map(data_list, ~model_fitter_rwdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))

@@

sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))

variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")

pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
                   off_diag_args = list(size = 0.75))
```
